Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-01-08 article.tex
Remove figure environments

\caption{First-order system of an exponential decay. The variable
\texttt{x} stores the initial condition for \(x\), and the variable
\texttt{eq} stores the rate equation for \(x\).}

@@

\caption{Second-order system of an harmonic oscillator, where the
variable \texttt{v} stores the derivative \(\frac{dx}{dt}\) and the rate
equation is specified for the derivative \texttt{v}.}

@@

\caption{First-order system of two exponential decays by composition of
the \texttt{Decay} system. The subsystem \texttt{linked} has a reference
to the outer variable \texttt{x}, while the subsystem
\texttt{independent} defines a new variable with initial condition §2\$,
which on the corresponding mathematical expression was named \(y\).}

@@

\[
\begin{align}
&\begin{cases}
    \frac{dA}{dt} = -2 \\
    \frac{dB}{dt} = +1
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
\]

@@

\[
\begin{align}
&\begin{cases}
    \frac{dA}{dt} = -2 A^2 \\
    \frac{dB}{dt} = +1 A^2
\end{cases}
\\\\
&\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\end{align}
\]

>>>>

\subcaption{First-order system of an exponential decay. The variable
\texttt{x} stores the initial condition for \(x\), and the variable
\texttt{eq} stores the rate equation for \(x\).}

@@

\subcaption{Second-order system of an harmonic oscillator, where the
variable \texttt{v} stores the derivative \(\frac{dx}{dt}\) and the rate
equation is specified for the derivative \texttt{v}.}

@@

\subcaption{First-order system of two exponential decays by composition of
the \texttt{Decay} system. The subsystem \texttt{linked} has a reference
to the outer variable \texttt{x}, while the subsystem
\texttt{independent} defines a new variable with initial condition §2\$,
which on the corresponding mathematical expression was named \(y\).}

@@

\[
\begin{cases}
    \frac{dA}{dt} = -2 \\
    \frac{dB}{dt} = +1
\end{cases}
\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\]

@@

\[
\begin{cases}
    \frac{dA}{dt} = -2 A^2 \\
    \frac{dB}{dt} = +1 A^2
\end{cases}
\begin{cases}
    A(0) &= 1 \\
    B(0) &= 0
\end{cases}
\]
